\renewcommand{\arraystretch}{1.2}
\begin{longtable}{|>{\raggedright\arraybackslash}p{3cm}|
                  >{\raggedright\arraybackslash}p{5cm}|
                  >{\raggedright\arraybackslash}p{5cm}|
                  >{\centering\arraybackslash}p{2cm}|}                  
\caption{System Functional Test Plan.}
\label{tab:test_plan} \\
\hline
\textbf{Test case} & \textbf{Steps} & \textbf{Expected Result} & \textbf{Status} \\
\hline
\endfirsthead
\endhead

Import employee data feature. & 
1. Navigate to Employee Profile → Import function.
\newline
2a. Upload valid Excel file with employee data.
\newline
2b. Upload invalid file (wrong format/missing columns).
\newline
2c. Upload file with duplicate employee codes, identities & 
1. Display user's managed departments in tree structure.
\newline
2a. Successfully import data, refresh employee list, show success message.
\newline
2b. Display specific error message (invalid format/missing required columns).
\newline
2c. Display error for duplicate entries, import only valid records. & 
PASS \\
\hline

Mark Student Attendance & 
1. Navigate to Attendance feature for selected class.
\newline
2. Mark students as present/absent/late.
\newline
3. Attempt to mark attendance for future dates.
\newline
4. Try to modify past attendance records.& 
1. Display student list with current attendance status.
\newline
2. Save attendance to database, send notifications to parents.
\newline
3. Future dates should be disabled in calendar.
\newline
4. Past records should be read-only.& 
PASS \\
\hline

Generate Student Attendance Report & 
1. Navigate to Student Attendance Report.
\newline
2. Select date range and generate report.
\newline
3. Export report to Excel format.
\newline
4. Try invalid date range. & 
1. Display departments managed by user.
\newline
2. Show attendance records with status indicators.
\newline
3. Download Excel file with formatted data.
\newline
4. Display validation error message. & 
PASS \\
\hline

Create Student Leave Requestt & 
1. Navigate to Leave Request feature.
\newline
2. Fill required fields and submit.
\newline
3. Create in leave request (overlapping, holiday conflicts, in valid date range). 
\newline
4. Submit request with missing mandatory fields or invalid field.& 
1. Display recent leave requests.
\newline
2. Save request, update student status, and send notification to teacher.
\newline
3. Display error message.
\newline
4. Disable submit button until all fields completed and valid.& 
PASS \\
\hline

Confirm Student Leave Request & 
1. Navigate to Confirm Leave request feature.
\newline
2. Review and approve/reject/revoke request.
\newline
3. Try to confirm expired leave request. & 
1. Display pending leave requests by priority.
\newline
2. Update request status, log approver info, and send notification to parents.
\newline
3. Show error for expired requests. & 
PASS \\
\hline

Post newsfeed & 
1. Navigate to Newsfeed feature.
\newline
2. Create post with text and images.
\newline
3. Upload attachments exceeding 100MB limit. 
\newline
4. Post with video content.& 
1. Display latest 10 newsfeed posts.
\newline
2. Save post, make visible to parents and teachers.
\newline
3. Display file size limit error. 
\newline
4. Successfully upload and display video content.& 
PASS \\
\hline

Confirm medicine reminder & 
1. Navigate to Medicine Reminder feature.
\newline
2. Confirm a valid reminder.
\newline
3. Try to confirm expired reminder. & 
1. Display latest 10 medicine reminders.
\newline
2. Update reminder status and send notification to parent.
\newline
3. Display error for expired reminders (usage date passed). & 
PASS \\
\hline

Real-time Bus Tracking & 
1. Navigate to Bus feature as parent.
\newline
2. Select bus route to track.
\newline
3. Transportation staff disables GPS.
\newline
4. No transportation staff assigned to route.& 
1. Display all active registered bus routes.
\newline
2. Establish WebSocket connection, receive real-time location updates every 50 meters.
\newline
3. Display GPS error message to parent.
\newline
4. Show "No staff assigned" error message.& 
PASS \\
\hline

\end{longtable}